Transparent Changes

### 2022-05-02 scripts/comparison.Rmd
Update plots

This script closely follows the preregistration, which is uploaded on OSF.

```{r setup}
# Packages used for the data workflow

@@

```{r}
# Moving time average
max_time_moving <- function(data, parameter) {
  spiro::spiro_max(data = data, smooth = parameter)$VO2_rel
}

@@

```{r calc}
# ZAN raw data only saves imprecise body mass data in the raw data file.
info <- read.csv("../data/participants.csv")

@@

write.csv(results, "../data/results.csv", row.names = FALSE)
```

@@

```{r}
res <- read.csv("../data/results.csv")

@@

```{r}
res_tidy <- pivot_longer(
  data = res_norm, 
  cols = !id,
  names_to = c("type", "parameter"),
  names_pattern = "(.*)_(.*)",
  names_transform = list(
    parameter = ~ as.numeric(.x),
    type = ~ factor(.x, 
      levels = c("bm", "tm", "tb"), 
      labels = c("moving breath", "moving time", "binned time")
    )
  )
)

@@

## Plot data: Comparison of processing strategies

```{r}
# Function for calculating quantils
quant <- function(data, lower, upper) {
  qs <- quantile(data, probs = c(lower, upper), names = FALSE)
  data.frame(
    ymin = qs[[1]],
    ymax = qs[[2]]
  )
}

ggplot(res_tidy, aes(x = parameter, y = perdiff, colour = type, fill = type)) +
  geom_hline(
    yintercept = 0,
    colour = "grey",
    alpha = 0.3
  ) +
  stat_summary(geom = "line", fun = "median") +
  stat_summary(
    geom = "ribbon", 
    fun.data = "quant", 
    fun.args = list(lower = 0.1, upper = 0.9),
    alpha = 0.1, 
    colour = NA
  ) +
  scale_x_continuous(
    name = "Parameter",
    breaks = c(15, 30, 45, 60)
  ) +
  scale_y_continuous(
    name = "% to Reference",
    labels = scales::percent,
    limits = c(-0.053,0.1)
  ) +
  scale_color_manual(
    values = met.brewer("Java", 3)
  ) +
  scale_fill_manual(
    values = met.brewer("Java", 3)
  ) +
  theme_classic() +
  theme(
    legend.position = c(0.8,0.8)
  )

ggsave("../plots/comparison.png", width = 6, height = 4, dpi = 600, bg = "white")
```

@@

```{r}
read_rr <- function(file) {
  dat <- spiro(file)
  # Zero-lag Butterworth filter with default parameters
  rr <- spiro_smooth(dat, smooth = "fz", columns = "RR")[, 1]
  time <- attr(dat, "raw")$time
  load <- attr(dat, "raw")$load

@@

ggsave(p_rr, filename = "../plots/rr.png", width = 6, height = 4, dpi = 600, bg = "white")
```

# Plot: Example of different strategies

```{r}
id <- 46
id_info <- read.csv("../data/participants.csv")
bodymass <- id_info$bodymass[id_info$p == id]

@@

exm_tidy$method <- factor(
  exm_tidy$method, 
  levels = c("raw", "mb", "mt", "tb", "fz"), 
  labels = c("raw", "Moving Breath", "Moving Time", "Binned Time", "Digital Filter")
)
exm_tidy$value <- exm_tidy$value / bodymass

ggplot(exm_tidy, aes(x = time)) +
  geom_point(data = exm_tidy[exm_tidy$method == "raw", ], aes(y = value), alpha = 0.1) +
  geom_line(data = exm_tidy[exm_tidy$method %in% c("Moving Time", "Moving Breath", "Digital Filter"), ], aes(y = value, color = method), size = 0.7) +
  geom_point(data = exm_tidy[exm_tidy$method == "Binned Time", ], aes(y = value, fill = method), color = met.brewer("Java", 3)[3], size = 1.2) +
  scale_x_continuous(
    name = "Time (min)",
    limits = c(500,850),
    breaks = c(540, 630, 720),
    labels = c(8, 10, 12),
    expand = c(0,0)
  ) +
  scale_y_continuous(
    name = "VO2 (ml/min/kg)",
    limits = c(55,75)
  ) +
  scale_color_manual(
    name = "",
    values = c(met.brewer("Java", 3)[1:2], "blue")
  ) +
   scale_fill_manual(
    name = "",
    values = "white"
  ) +
  theme_classic() +
  theme(
    legend.position = c(0.9, 0.55),
  )

ggsave(filename = "../plots/example.png", width = 6, height = 4, dpi = 1200, bg = "white")
```

>>>>

This script closely follows the preregistration, which is uploaded on the [OSF](https://osf.io/3am4s).

```{r setup, warning = FALSE, message = FALSE}
knitr::opts_chunk$set(out.width = "70%", fig.align = "center")

# Packages used for the data workflow

@@

```{r fuctions}
# Moving time average
max_time_moving <- function(data, parameter) {
  spiro::spiro_max(data = data, smooth = parameter)$VO2_rel
}

@@

```{r calc, eval = FALSE}
# ZAN raw data only saves imprecise body mass data in the raw data file.
info <- read.csv("../data/participants.csv")

@@

# write.csv(results, "../data/results.csv", row.names = FALSE)
```

@@

```{r norm}
res <- read.csv("../data/results.csv")

@@

```{r wrangle}
res_tidy <- pivot_longer(
  data = res_norm, 
  cols = !id,
  names_to = c("type", "parameter"),
  names_pattern = "(.*)_(.*)",
  names_transform = list(
    parameter = ~ as.numeric(.x),
    type = ~ factor(.x, 
      levels = c("bm", "tm", "tb"), 
      labels = c("Moving Breath", "Moving Time", "Binned Time")
    )
  )
)

@@

## Plot: Comparison of processing strategies

```{r comparison, warning = FALSE}
# Function for calculating quantiles
quant <- function(data, lower, upper) {
  qs <- quantile(data, probs = c(lower, upper), names = FALSE)
  data.frame(
    ymin = qs[[1]],
    ymax = qs[[2]]
  )
}

p_comp <- ggplot(res_tidy, aes(x = parameter, y = perdiff, colour = type, fill = type)) +
  geom_hline(
    yintercept = 0,
    colour = "grey",
    alpha = 0.3
  ) +
  stat_summary(geom = "line", fun = "median") +
  stat_summary(
    geom = "ribbon", 
    fun.data = "quant", 
    fun.args = list(lower = 0.1, upper = 0.9),
    alpha = 0.1, 
    colour = NA
  ) +
  scale_x_continuous(
    name = "Parameter",
    breaks = c(15, 30, 45, 60)
  ) +
  scale_y_continuous(
    name = "% to Reference",
    labels = scales::percent,
    limits = c(-0.053,0.1)
  ) +
  scale_color_manual(
    name = "Processing Strategy",
    values = met.brewer("Java", 3)
  ) +
  scale_fill_manual(
    name = "Processing Strategy",
    values = met.brewer("Java", 3)
  ) +
  theme_classic() +
  theme(
    legend.position = c(0.8,0.8)
  )

# ggsave("../plots/comparison.png", plot = p_comp, width = 6, height = 4, dpi = 600, bg = "white")

knitr::include_graphics("../plots/comparison.png")
```

@@

```{r rr}
read_rr <- function(file) {
  dat <- spiro(file)
  # Zero-lag Butterworth filter with default parameters
  rr <- spiro_smooth(dat, smooth = "fz", columns = "RR")[, 1]
  time <- attr(dat, "raw")$time
  load <- attr(dat, "raw")$load

@@

# ggsave(filename = "../plots/rr.png", plot = p_rr, width = 6, height = 4, dpi = 600, bg = "white")

knitr::include_graphics("../plots/rr.png")
```

## Plot: Example of different strategies

```{r example, warning = FALSE}
id <- 46
id_info <- read.csv("../data/participants.csv")
bodymass <- id_info$bodymass[id_info$p == id]

@@

exm_tidy$method <- factor(
  exm_tidy$method, 
  levels = c("raw", "mb", "mt", "tb", "fz"), 
  labels = c("raw","Moving Breath","Moving Time","Binned Time", "Digital Filter"),
  ordered = TRUE
)
exm_tidy$value <- exm_tidy$value / bodymass

p_ex <- ggplot(exm_tidy, aes(x = time)) +
  geom_point(data = exm_tidy[exm_tidy$method == "raw", ], aes(y = value), alpha = 0.1) +
  geom_line(data = exm_tidy[exm_tidy$method %in% c("Moving Breath", "Moving Time", "Digital Filter"), ], aes(y = value, color = method), size = 0.7) +
  geom_point(data = exm_tidy[exm_tidy$method == "Binned Time", ], aes(y = value, fill = method, colour = "Binned Time"), size = 1.4) +
  scale_x_continuous(
    name = "Time (min)",
    limits = c(500,860),
    breaks = c(540, 630, 720),
    labels = c(8, 10, 12),
    expand = c(0,0)
  ) +
  scale_y_continuous(
    name = "VO2 (ml/min/kg)",
    limits = c(55,75)
  ) +
  scale_color_manual(
    name = "Processing Strategy",
    values = c(met.brewer("Java", 3)[3], "blue", met.brewer("Java", 3)[c(1,2)]),
    labels = c("Binned Time", "Digital Filter","Moving Time","Moving Breath"),
    guide = guide_legend(
      reverse = TRUE,
      override.aes = list(
        linetype = c(rep.int("solid", 3), "blank"),
        shape = c(rep.int(NA, 3), 19),
        color = c(met.brewer("Java", 3)[c(1,2)], "blue", met.brewer("Java", 3)[3])
      )
    )
  ) +
   scale_fill_manual(
    values = "white",
    guide = "none"
  ) +
  theme_classic() +
  theme(
    legend.position = c(0.88, 0.6),
  )

# ggsave(filename = "../plots/example.png", plot = p_ex, width = 6, height = 4, dpi = 1200, bg = "white")

knitr::include_graphics("../plots/example.png")
```

### 2022-05-02 scripts/review.Rmd
Update plots

# ggsave(p_int, "../plots/duration_count.png", width = 5, height = 3, dpi = 600, bg = "white")

@@

# ggsave(p_strat, "../plots/strategies.png", width = 5, height = 3, dpi = 600, bg = "white")

>>>>

# ggsave("../plots/duration_count.png", plot = p_int, width = 5, height = 3, dpi = 600, bg = "white")

@@

# ggsave("../plots/strategies.png", plot = p_strat, width = 5, height = 3, dpi = 600, bg = "white")
